### 2025-07-19 modern-portfolio-theory.qmd
20250718 - citations

Even so-called experts do not beat the market reliably.
There is little consistency in the performance of mutual fund managers over time.
In the book, "The Drunkard's Walk: How Randomness Rules Our Lives", @Mlodinow2008 reported essentially no correlation between performance of the top mutual funds in a five-year period with their performance over the subsequent five years.
That is, the best funds in a one period were not necessarily the best funds in another period.
This suggests that mutual fund managers differ in great part because of luck or chance rather than reliable skill.
In any given year, some mutual funds will do better than other mutual funds.
But this overperformance in a given year likely reflects more randomness than skill.
That is likely why [a cat beat professional investors in a stock market challenge](http://www.npr.org/blogs/money/2013/01/14/169326326/housecat-beats-investors-in-stock-market-challenge) [@Goldstein2013; archived at <https://perma.cc/R3XU-K6J8>].
That is, "few stock pickers, if any, have the skill needed to beat the market consistently, year after year" [@Kahneman2011, p. 214].
Although our sample size is much smaller with fantasy football projections, there also appears to be little consistency in fantasy football sites' rank in accuracy over time [INSERT], suggesting that the projection sources are not reliably better than each other (or the crowd) over time.

The market reflects all of the knowledge of the crowd.
One common misconception is that if you go with the market, you will receive "average" returns (by "average", I mean that you will be in the 50th percentile among investors).
This is not true—it has been shown that most mutual funds (about 80%) underperform the average returns of the stock market.
So, by going with the market average, you will likely perform better than the "average" fund/investor.
Consistent with this, crowd-averaged fantasy football projections tend to be more accurate than any individual's projection: INSERT
This evidence is consistent with the notion of the [wisdom of the crowd](#sec-wisdomOfCrowd), described in @sec-wisdomOfCrowd.
Moreover, even if the stock market is relatively accurate ("efficient") in terms of valuing stocks based on all (publicly) available information (i.e., the efficient market hypothesis), your fantasy football league is likely not.
Thus, it may be effective to use crowd-based projections to identify players who are undervalued by your league.

>>>>

Even so-called experts do not beat the market reliably.
There is little consistency in the performance of mutual fund managers over time.
In the book, "The Drunkard's Walk: How Randomness Rules Our Lives", @Mlodinow2008 reported essentially no correlation between performance of the top mutual funds in a five-year period with their performance over the subsequent five years.
That is, the best funds in a one period were not necessarily the best funds in another period.
This suggests that mutual fund managers differ in great part because of luck or chance rather than reliable skill.
In any given year, some mutual funds will do better than other mutual funds.
But this overperformance in a given year likely reflects more randomness than skill.
That is likely why [a cat beat professional investors in a stock market challenge](http://www.npr.org/blogs/money/2013/01/14/169326326/housecat-beats-investors-in-stock-market-challenge) [@Goldstein2013; archived at <https://perma.cc/R3XU-K6J8>].
That is, "few stock pickers, if any, have the skill needed to beat the market consistently, year after year" [@Kahneman2011, p. 214].
Although our sample size is much smaller with fantasy football projections, there also appears to be little consistency in fantasy football sites' rank in accuracy over time [@Kartes2024; archived at <https://perma.cc/69F7-LLTN>; @Petersen2017; archived at <https://perma.cc/BG2W-ANUF>], suggesting that the projection sources are not reliably better than each other (or the crowd) over time.

The market reflects all of the knowledge of the crowd.
One common misconception is that if you go with the market, you will receive "average" returns (by "average", I mean that you will be in the 50th percentile among investors).
This is not true—it has been shown that most mutual funds (about 80%) underperform the average returns of the stock market.
So, by going with the market average, you will likely perform better than the "average" fund/investor.
Consistent with this, crowd-averaged fantasy football projections tend to be more accurate than any individual's projection [@Kartes2024; archived at <https://perma.cc/69F7-LLTN>; @Petersen2017; archived at <https://perma.cc/BG2W-ANUF>].
This evidence is consistent with the notion of the [wisdom of the crowd](#sec-wisdomOfCrowd), described in @sec-wisdomOfCrowd.
Moreover, even if the stock market is relatively accurate ("efficient") in terms of valuing stocks based on all (publicly) available information (i.e., the efficient market hypothesis), your fantasy football league is likely not.
Thus, it may be effective to use crowd-based projections to identify players who are undervalued by your league.
